---
title: "R Notebook"
output: html_notebook
---

# Introduction

In the following markdown file, I will be cleaning the World Development Indicators data set in preparation for a visualization in Tableau. This data contains presents the most current and accurate global development data available, and includes national, regional and global estimates.


Raw data, which has been last updated on 4/9/2020, can be found here from the [World Bank group](https://datacatalog.worldbank.org/dataset/world-development-indicators)

# Data Preview
```{r}
#Set working directory
##knitr::opts_knit
work_dir <- "C:/Users/kishe/Documents/Data Science/Projects/Tableau/Makeover Monday/World Development Indicators"

setwd(work_dir)

list.files()
```
### Read in libraries
```{r echo=TRUE, results='hide'}
#Read in libraries
library(tidyverse)
```

### Read in Data
```{r}
#Read in raw data
list.files()
```


```{r}
getwd()
```


```{r}
```
*Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
